Evaluating infectious disease forecasts with allocation scoring rules

### 2023-05-15 alloscore_manuscript/allocation.tex
adding update for intro paragaph 4. latex still not working quite right for me tho.

In practice, probablistic infectious disease forecasts have most often been evaluated with standard, off-the-shelf scoring rules such as the log score, continuous ranked probability score (CRPS), or weighted interval score (WIS). [cite some examples] While some of these scores can be interpreted through the lens of decision theory [thinking here of WIS/quantile loss], these connections are not a common focus of infectious disease forecast evaluation.

>>>>

In practice, probablistic infectious disease forecasts have most often been evaluated with standard, ``off-the-shelf'' scoring rules.
For example, seasonal influenza forecasts in the US and dengue forecasts for Peru and Puerto Rico used log-score to evaluate forecast skill \cite{mcgowan_collaborative_2019,reich_collaborative_2019,johansson_open_2019}.
Pandemic COVID-19 forecasts in the US and Europe were evaluated using the weighted interval score (WIS), an approximation of the continuous ranked probability score (CRPS), and prediction interval coverage\cite{cramer_evaluation_2022}.
Similarly, CRPS was also used to assess probabilistic forecasts of dengue outbreaks in Vietnam\cite{colon-gonzalez_probabilistic_2021}.
While some of these scores can be interpreted through the lens of decision theory, and all of the application-specific papers cited above had authors from public health agencies, none of them make explicit connections between a forecast evaluation and how a forecast was used in practice.
In general, explicit links between how forecasts are evaluated and how they are scored are not a common focus of infectious disease forecast evaluations.
